### 2018-10-26 README.Rmd
remove errant ,

    @Manual{drtmlepackage,
      title = {drtmle: Doubly-Robust Nonparametric Estimation and Inference},
      author = {David Benkeser},
      note = {R package version 1.0.0},
      doi = {10.5281/zenodo.844836},
    }

>>>>

    @Manual{drtmlepackage,
      title = {drtmle: Doubly-Robust Nonparametric Estimation and Inference},
      author = {David Benkeser},
      note = {R package version 1.0.0},
      doi = {10.5281/zenodo.844836}
    }
